### 2021-05-14 docs/manuscript/PLOS-MSc-Thesis.tex
Describe properly supplementary fig: expression of topol 9

\paragraph*{S1 Fig.}
\label{S2_Fig}
{\bf Dynamics of expression of topology number 9.}

>>>>

\paragraph*{S1 Fig.}
\label{S2_Fig}
{\bf Dynamics of expression of topology number 9.}
The dynamics of expression is shown from $t = 5$ to $t = 150$. The red line
represents the expression level of the gene C along the morphogenetic field,
whereas the dotted line represents the expression level of gene A. The
striped pattern of gene expression can be seen for both genes since $t = 80$.
